\ \break Automatikus korpuszépítés tulajdonnév-felismerés céljára

### 2013-01-04 paper/MSZNY2013/mszny_slides.tex
3 slides assigned to ppl.
Hahaha!

@@

%\begin{frame}{The Hungarian Corpus}
%  The algorithm is, in theory, language-agnostic. We tested this property by
%  applying it to a medium-sized language, Hungarian. \\
%  Difference from bigger, well-resourced languages:
%  \begin{itemize}
%  \vitem E % TODO: ide mit?
%  \end{itemize}
%\end{frame}

%TODO: the "Hungarian Corpus" phrase must appear in the frame title 
\begin{frame}{Nyelvfüggetlenség}
\end{frame}

\begin{frame}{Differences from English}
  \bigskip
  \begin{itemize}
  \vitem Language processing tools
    \begin{itemize}
    \vitem Inflectional morphology: different set of tools were needed 
    \vitem We developed a flexible framework that enables the plugging of any NLP tool
    % TODO: what kind of linguistic tools are needed: table?
    \end{itemize}
  \vitem Wikipedia size and coverage
    \begin{itemize}
    \vitem Hungarian is medium-size language: \nagytilde 200k articles vs.~\nagytilde 4M English pages
    \vitem Cross-references may point to English pages
    \vitem Templates are in Hungarian: per-language template configuration
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Differences from English -- cont.}
  \bigskip
  \begin{itemize}
  \vitem DBpedia coverage
    \smallskip
    \begin{itemize}
    \vitem Internationalized chapters for big languages only
    \vitem "Hungarian" DBpedia list contains English articles % Nem egyértelmű
      \begin{itemize}
      \vitem Hungarian equivalents must be added to the list % Added: lásd előző oldal 2/2
      \vitem Hungarian entities without an English page are missing:
             the NER language model might not be accurate
      \vitem Future work: extend the list with the missing Hungarian entities
      \end{itemize}
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}{Differences from English -- cont.}
  \bigskip
  \begin{itemize}
  \vitem NE conventions
    \smallskip
    \begin{itemize}
    \vitem Szeged NER guideline: similar to CoNLL
    \vitem Common nouns in Hungarian: names of languages, religions, months, etc. \nyil more consistent MISC category
    \vitem NEs can be subject of compounding \nyil the joint common noun can modify the original sense and category of the NE:
    \end{itemize}
  \end{itemize}
  \bigskip
  \begin{Examplee}
  \small{WorldCom {\normalfont(\texttt{ORG})} \nyil WorldCom-botrány ['WorldCom scandal'] {\normalfont(\texttt{O})}}
  \end{Examplee}
\end{frame}

>>>>

\begin{frame}{Nyelvfüggető elemek}
  \bigskip
  \begin{itemize}
  \vitem Nyelvi eszközök
    \begin{itemize}
    \vitem kidolgoztunk egy keretrendszert, amibe bármilyen eszközt be lehet kötni
    \vitem tokenizáló, lemmatizáló, szófajmeghatározó
    \end{itemize}
  \vitem Wikipédia
    \begin{itemize}
    \vitem Sablonok nyelvfüggőek
    \vitem a magyar egy közepes méretű nyelv: \nagytilde 200k cikk a kb.~\nagytilde 4M angollal szemben
    \end{itemize}
  \vitem DBpedia
    \begin{itemize}
    \vitem nagyobb nyelvekre honosított fejezetek --- magyarra nincs
    \vitem csak az angol Wikipédiában is szereplő magyar tulajdonneveket tartalmazza
    \vitem távlati terv a lista kiegészítése gépi tanulással  % TODO "Future work"
    \end{itemize}
  \end{itemize}
\end{frame}

@@

% Eszter
% TODO a következő fejezetbe
\begin{frame}{Differences from English -- cont.}
  \bigskip
  \begin{itemize}
  \vitem NE conventions
    \smallskip
    \begin{itemize}
    \vitem Szeged NER guideline: similar to CoNLL
    \vitem Common nouns in Hungarian: names of languages, religions, months, etc. \nyil more consistent MISC category
    \vitem NEs can be subject of compounding \nyil the joint common noun can modify the original sense and category of the NE:
    \end{itemize}
  \end{itemize}
  \bigskip
  \begin{Examplee}
  \small{WorldCom {\normalfont(\texttt{ORG})} \nyil WorldCom-botrány ['WorldCom scandal'] {\normalfont(\texttt{O})}}
  \end{Examplee}
\end{frame}
